Precise Data Flow Analysis\\in the Presence of Correlated Method Calls

### 2015-06-08 sas2015/response.txt

We thank the reviewers for their insightful and helpful comments.

Reviewer 1 asks two important questions: why we are comparing the correlated-calls (CC) analysis to the equivalence-IDE analysis, and why do we not compare the CC analysis to the IFDS analysis instead. 
We will emphasize in the revised version that the equivalence analysis is there for two reasons: 
i) to explain how a CC-IDE problem can be derived from an IDE problem that has the same meaning as the original IFDS problem; 
ii) to provide a base line against which to compare the efficiency of the CC analysis. 
We compare the efficiency of the CC-analysis against the equivalence-IDE analysis instead of the IFDS analysis because the time complexities of an IFDS and an equivalent IDE analysis are the same: an equivalent IDE analysis is just an IFDS analysis in which all edges are labeled with identity micro functions, and all operations on those functions are optimized to be constant-time. We will also add this clarification to Section 4.7.

Reviewer 1 mentions that in Table 2, it would be useful to include numbers to reflect the exact precision improvement of the correlated-calls analysis. As we discussed in Section 4.7, for the particular combination of taint analysis and the SPEC JVM’97 benchmarks, we did not observe a gain in precision. These numbers were presented to show that the running time of the analysis is reasonable. Reviewer 1 also suggests moving Table 2 to Section 4.7; we will do so if space permits.

Reviewer 2 points out interesting related work by Isil Dillig on data-flow analysis that handles missing libraries. We will read and address this work in the Related Work section. We will also revise that section to include a more detailed comparison to context sensitivity, as Reviewer 3 requests, in particular related to the Cartesian Product Algorithm.

Reviewer 1 and 3 made several insightful suggestions to improve the readability of the paper. We will address minor issues (clarifications, notation, and formatting) in the revised version.

### 2015-06-08 sas2015/content/related.tex
added CPA reference

Our approach superficially resembles, but is orthogonal, to context
sensitivity, including such variations as object sensitivity~\cite{DBLP:conf/issta/MilanovaRR02,DBLP:journals/tosem/MilanovaRR05}.
Context-sensitive
points-to analysis is orthogonal to our work because it analyzes the
flow of data (pointers), whereas we analyze control flow paths.
Also, object-sensitive points-to analysis is flow-insensitive, while
IFDS and IDE are flow-sensitive analyses. Note that our transformation only makes sense
in a flow-sensitive setting since a flow-insensitive analysis already
introduces many infeasible control flow paths.

>>>>

Our approach superficially resembles, but is orthogonal, to context
sensitivity, including the CPA algorithm~\cite{Agesen:95} and such variations as object sensitivity~\cite{DBLP:conf/issta/MilanovaRR02,DBLP:journals/tosem/MilanovaRR05}.
Context-sensitive
points-to analysis is orthogonal to our work because it analyzes the
flow of data (pointers), whereas we analyze control flow paths.
Also, object-sensitive points-to analysis is flow-insensitive, while
IFDS and IDE are flow-sensitive analyses. Note that our transformation only makes sense
in a flow-sensitive setting since a flow-insensitive analysis already
introduces many infeasible control flow paths.
